%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Russell's Resume
% LaTeX v
%
% You're welcome to copy this
% I'm no designer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%       Setup
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{rrollins-res}

\usepackage[document]{ragged2e}
\usepackage[left=0.75in, top=0.35in, right=0.75in, bottom=0.35in]{geometry} %set margins
\usepackage[hidelinks]{hyperref}

\hyphenpenalty=10000
\exhyphenpenalty=10000



\name{Russell A. Rollins} % My Name
\address{296 Eleanor St SE \\ Atlanta, GA 30317}
        {p: (904)-304-0822 e: \href{mailto:russell@russellrollins.com}{russell@russellrollins.com} w: \href{https://russellrollins.com}{russellrollins.com}} %The two address lines
        {U.S. Citizen}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%      Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\roottitle{EXPERIENCE}

\headedsection
{Pardot}
{Atlanta, GA} {

\headedsubsection
{Lead Member of Technical Staff, BREAD Team}
{October 2021 -- Present}
{\bodytext{\begin{itemize}

\item \textbf{Tech lead for Terraformer, Pardot's internal Terraform-as-a-Service platform (written in Go).} 25 infrastructure engineers use it to manage 20 Kubernetes clusters and 1,000 EC2 instances and it has been a core reason Pardot infrastructure runs with one of the lowest cost-to-serve profiles and lowest change-failure rates at Salesforce. On shared on-call for BREAD's services.

\item \textbf{Designed and shipped Terraformer's plan-review UI}, turning mandatory plan review from a social convention into an enforced gate (load-bearing for SOC 2 audit after an unreviewed plan caused an incident).

\item \textbf{Built multi-version support and per-VPC job dispatch.} Multi-version ended a years-long lock on Terraform 0.12 (current on every release since); per-VPC dispatch is a gRPC service that runs plans inside target VPCs instead of the shared control-plane VPC, reducing blast radius and putting firewall-isolated services like Consul and Vault under Terraform's management.

\item \textbf{Led a cross-team migration of Docker base images from mutable to immutable tags}, closing a major compliance risk while auto-generated upgrade PRs kept upgrades painless for service teams.

\end{itemize}

}}

}

\headedsection
{HashiCorp}
{Remote (Atlanta, GA)} {

\headedsubsection
{Senior Engineer, Engineering Services}
{October 2018 -- September 2021}
{\bodytext{\begin{itemize}

\item \textbf{Release Engineer for Terraform Cloud, HashiCorp's hosted Terraform service.} TFC monetizes running customer Terraform code, which is both its value prop and its core operational problem: platform deploys were slow and manual, and customer-execution (effectively a webhook-to-RCE surface) ran on expensive ephemeral EC2 VMs.

\item \textbf{Built a deployment manifest system tying CI into the deploy bot}, replacing a manual process where engineers copied UUIDs from CI logs into chat. Most deploys became fully automated; the rest dropped to a one-line chat command.

\item \textbf{Designed and built a new customer execution platform for Terraform Cloud}: gVisor-isolated containers on Nomad, replacing per-customer ephemeral EC2 VMs. The new platform was cheaper to operate and scaled faster, and selling customers more CPU or memory became a Nomad config change rather than a per-customer EC2 buildout (all-but-impossible under the old model). gVisor's userland-syscall sandbox preserved the multi-tenant isolation that customer code execution requires.

\end{itemize}

}}

}

\headedsection
{Pardot}
{Atlanta, GA} {

\headedsubsection
{Member / Sr. Member of Technical Staff, BREAD Team}
{June 2016 -- October 2018}
{\bodytext{\begin{itemize}

\item \textbf{DevOps engineer on Pardot's BREAD team, the internal tooling group that scaffolded the company's lift-and-shift from Salesforce data centers to AWS.} Wrote most of the original Terraformer codebase (shared state, locking, secrets) to onboard the Pardot Infrastructure team to Terraform.

\end{itemize}

}}

\headedsubsection
{Associate Member / Member of Technical Staff, New Markets Team}
{June 2015 -- June 2016}
{\bodytext{\begin{itemize}

\item \textbf{Application engineer on Pardot's Engagement Studio, the customer-facing system that powered drip campaigns to millions of prospects.} Wrote Automation Rules across the legacy PHP application and the new Kafka/Storm Java stack.

\end{itemize}

}}

}

\headedsection
{Internships during Computer Engineering studies}
{\emph{2012 -- 2014}} {

\bodytext{\begin{itemize}

\item \textbf{BAE Systems} (San Diego, CA), Jun -- Aug 2014: automatic test equipment software for F-16 aircraft.

\item \textbf{Umenta} (Atlanta, GA), Jan -- Aug 2013: PHP/JavaScript at a CMS startup, alongside classes.

\item \textbf{Georgia Tech Research Institute} (Atlanta, GA), May -- Dec 2012: C\# desktop and Sencha Touch mobile development on Chemical Companion, an emergency-response field tool.

\end{itemize}

}

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%       Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\roottitle{EDUCATION}

\headedsection
{The Georgia Institute of Technology}
{Atlanta, GA} {

\headedsubsection
{B.S. Computer Engineering}
{August 2011 -- May 2015}
{\bodytext{\begin{itemize}

\item Specialization in Systems and Controls with Applications in Robotics
\item Cumulative GPA 3.74

\end{itemize}

}}

}

\end{document}
